% !TeX root = ../resume.tex
\section{Experience}
\begin{entrylist}

    \item \textbf{\href{https://www.we-plus.asia/}{We-plus HK Ltd.}} \hfill Hong Kong\\
    Analyst Programmer - CLP Power Hong Kong DNOO Project \hfill April 2025--Aug 2025\\

    \begin{detaillist}
    \item Managed data migration and validation for statistical reports and databases \textbf{within a 5-month timeline}, redesigning legacy reports and data tables on the new database, and achieving zero discrepancies.
    \item Developed automated \textbf{Python} validation tools to ensure data consistency across DMS, ADMS, and SCADA systems; created data mapping logic and \textbf{validation program} to reduce manual reconciliation efforts.
    \end{detaillist}

    \item \textbf{\href{https://www.infa.com/}{ST Engineering INFA Systems Ltd.}} \hfill Hong Kong\\
    System Engineer of HKFSD-4GMS-IMS - Senior Associate Engineer \hfill Oct 2023--Apr 2025\\
    Hong Kong Fire Services Department – Fourth Generation Mobilising System (4GMS)\\

    \begin{detaillist}
        \item Focused on the \textbf{system integration across various IMS components, and collaborating with developer and goverment clients.}
        \item \textbf{Achieved the highest ticket resolution rate in the team. Resolved 250+ system issue tickets}, and executed 80+ test cases within 1.5 years; managed 12 IMS components with hands-on experience across DevOps platforms (\textbf{Azure DevOps}), databases (\textbf{Oracle, MariaDB, SQL Server}), monitoring tools (\textbf{eG Innovations, Kafka-UI}), and system administration (\textbf{Windows ADDS, Ubuntu, Nginx, Docker}).
        \item Assisted in \textbf{data migration of 30+ legacy reports} to new IMS platform; reproduced statistical reports with new data structure and \textbf{built database objects (views, stored procedures, PL/SQL, SSRS)} to ensure data conversion, accuracy, and improved query performance.
    \end{detaillist}

    \item \textbf{\href{https://www.crbank.com.cn/}{China Resources Bank of Guangdong}} \hfill Shenzhen, CN\\
    Data Development Engineer \hfill May 2021--Sep 2022\\

    \begin{detaillist}
        \item Data Warehouse \& BI Development: Participated in \textbf{data warehouse construction across traditional (Oracle DB, SQL, Perl, BMC Control-M, Oracle BIEE), big data (HiveQL/HUE, DaVinci on Hadoop), and cloud platforms (Alibaba Cloud Dataphin, QuickBI)}. Designed dimensional models, managed data layers (ODS to BI), and used GitLab for version control.

        \item BI Reporting \& Data Pipelines: Built \textbf{30+ BI reports and 50+ data pipeline scripts} across all platforms to support personal loan statistics and financial monitoring. Automated ETL workflows with BMC Control-M.

        \item Cross-platform Data Support: Fulfilled 18 data mining requirements by extracting and preparing data for business users, analytics, and machine learning teams.

    \end{detaillist}

    \item \href{https://skhongkongltd.com/}{\textbf{SK Hong Kong Ltd.}} \hfill  Hong Kong\\
    IT Administrator \hfill Oct 2025--Present\\

    \begin{detaillist}
        \item Collaborated with CTO on strategy; led \textbf{AWS FinOps} (resource rightsizing, savings plans, reservation instances) and administration with \textbf{CloudWatch metrics}. Managed \textbf{Azure} cross-tenant issues and coordinated cross-region IT with UK, Romania, Dubai, India, and European teams. AWS stack: \textbf{EC2, IAM, CloudTrail, CloudWatch}.

        \item Managed \textbf{Microsoft Azure, 365, Teams Administration}, and office IT infrastructure (VPN, internal systems).

        \item Power Platform Development: Built \textbf{Power BI dashboards} tracking project progress with \textbf{Power Automate RPA workflows} to integrate MS Planner data, and \textbf{automated file management} on office-policy document approvals.
    \end{detaillist}
\newpage
    \item \textbf{\href{https://www.etnet.com.hk/}{ET Net Ltd.}} \hfill Hong Kong\\
    Web Developer \hfill Jan 2020--Apr 2021\\
    \begin{detaillist}
        \item Developed and maintained financial web applications using \textbf{JavaScript, HTML/CSS, PHP and MySQL}. Implemented new features and optimized performance based on user feedback and analytics.
        \item Collaborated with cross-functional teams to design and implement \textbf{RESTful APIs for data integration with third-party services}. Utilized Git for version control and participated in code reviews to ensure code quality and adherence to best practices.
    \end{detaillist}

    \item \textbf{\href{https://www.mitac.com.tw/}{Mitac Information Tech. Corp.}} \hfill Taipei\\
    Assistant Engineer - Internship \hfill Jul 2019--Dec 2020\\

    \begin{detaillist}
    \item Participated in \textbf{Taiwan's government system development and testing for automotive applications, implementing features and bug fixes using C\#, ASP.NET MVC, and Oracle SQL.}
    \item Conducted software testing and validation, including writing test cases and documenting results; collaborated with senior engineers to troubleshoot issues and optimize system performance.
    \end{detaillist}

\end{entrylist}
