%====================
% EXPERIENCE D
%====================
\subsection{{IT Administrator \hfill Oct 2025 --- Present}}
\subtext{\href{https://skhongkongltd.com/}{SK Hong Kong Ltd. \hfill Hong Kong}}
\begin{zitemize}
    \item Managed \textbf{Microsoft Azure, AWS Cloud, O365 ecosystem, Power Platform}, and office IT infrastructure (Azure Entra(AD), Intune, AWS IAM, VPN, printers, projectors, and AV systems)
    \item Collaborated with CTO on strategy; led \textbf{AWS FinOps} (rightsizing EC2,RDS , purchase savings plans, and RIs), built AWS-CloudWatchAgent with SSM and cloudshell to monitor resource usages. Coordinated cross-region IT with UK, Romania, Dubai, India, and European teams. 
\item Automating file management, email notifications, and MS Planner data pipeline with \textbf{Power Automate achieved task progress-tracking dashboards and automated office approval processes.}

\end{zitemize}
%====================
% EXPERIENCE A
%====================
\subsection{{Analyst Programmer / CLP Power Hong Kong DNOO Project \hfill Apr 2025 --- Aug 2025}}
\subtext{\href{https://www.we-plus.asia/}{We-plus HK Ltd. \hfill Hong Kong}}
\begin{zitemize}
    \item Developed automated \textbf{Python} validation program, data mapping logic to ensure data consistency across DMS, ADMS, and SCADA systems to reduce manual reconciliation efforts.
    \item Performed data migration and validation for SSRS reports and databases within a 5-month timeline, reproduced legacy reports and data ingestion logic on the new system.
\end{zitemize}
%====================
% EXPERIENCE B
%====================
\subsection{{System Engineer / HKFSD - Fourth Generation Mobilising System \hfill Oct 2023 --- Apr 2025}}
\subtext{\href{https://infa.com/}{ST Engineering INFA Systems Ltd. \hfill Hong Kong}}
\begin{zitemize}
    \item \textbf{System integration, maintenance,configuration, troubleshooting across 4GMS-IMS, and collaborating with developers and HKFSD}. Led IMS functional testing, integration test execution(SFT, SIT), and test specification documentation. Performed daily health check, system upgrade, patches, and enhancements. Ensured consistent communication and data across all subsystems. \textbf{Achieved the highest issue-resolution rate in the team. Resolved 250+ system tickets and executed 80+ test cases within 1.5 years.}
    \item \textbf {Integrated and managed business logic of 12 IMS components(FS276 incident report, Incident Information Dissemination Mechanism(IIDM), HKO-OpenAPI etc.)} with hands-on experience across DevOps platforms (\textbf{Azure DevOps}), databases (Oracle, MariaDB, SQL Server), monitoring tools(eG Innovations, Kafka-UI), and system administration (Windows Server/ADDS, Ubuntu, Nginx, Docker, NextCloud, Fortinet, TCP/IP firewall).
    \item Assisted in data migration of 30+ legacy SSRS reports to IMS: \textbf{Constructed data pipeline by views, stored procedures, functions with PL/SQL to reproduce the legacy statistical reports}, simultaneously ensuring data conversion, accuracy, and \textbf{improved query performance}.
\end{zitemize}
%====================
% EXPERIENCE C
%====================
\subsection{{Data Development Engineer / Data Management Dept. \hfill Feb 2021 --- Sep 2022}}
\subtext{\href{https://www.crbank.com.cn/}{China Resources Bank of Guangdong Co. Ltd. \hfill Shenzhen, China}}
\begin{zitemize}
    \item \textbf{Data Warehouse \& BI Development across traditional (Oracle DB, SQL, Perl, BMC Control-M, Oracle BIEE), big data (HiveQL/HUE, DaVinci on Hadoop), and cloud platforms (Alibaba Cloud Dataphin, QuickBI). Designed dimensional models, managed data layers (ODS to BI), and used GitLab for version control.
    \item Built 30+ BI reports and 50+ Data pipelines across all platforms to support personal loan statistics and financial monitoring. Automated ETL workflows with BMC Control-M.
    \item Data mining support for analysts and machine learning teams.}
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{{Web Developer / etnet.com.hk \hfill Aug 2020 --- Feb 2021}}
\subtext{\href{https://www.etnet.com.hk/}{ET Net Ltd. \hfill Hong Kong}}
\begin{zitemize}
        \item Developed and maintained financial web applications using \textbf{JavaScript, HTML/CSS, PHP and MySQL}. Implemented new features and optimized performance based on user feedback and analytics.
        \item Collaborated with cross-functional teams to design and implement \textbf{RESTful APIs for data integration with third-party services}. Utilized Git for version control and participated in code reviews to ensure code quality and adherence to best practices.
\end{zitemize}

%====================
% EXPERIENCE F
%====================

\subsection{{Assistant Engineer / Internship \hfill Jul 2019 --- Dec 2020}}
\subtext{\href{https://www.mitac.com.tw/}{Mitac Information Tech. Corp. \hfill Taipei, TW}}
\begin{zitemize}
    \item Participated in Taiwan's government system development and testing for automotive applications, implementing features and bug fixes using \textbf{C\#, ASP.NET MVC, and Oracle SQL.}
    \item Conducted software testing and validation, including writing test cases and documenting results; collaborated with senior engineers to troubleshoot issues and optimize system performance.
\end{zitemize}

%====================
% EXPERIENCE G
%====================
%\subsection{{ROLE / PROJECT G \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company G \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE H
%====================
%\subsection{{ROLE / PROJECT H \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company H \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}

%====================
% EXPERIENCE I
%====================
%\subsection{{ROLE / PROJECT I \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company I \hfill somewhere, state}
%\begin{zitemize}
%    \item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%    \item Ut malesuada purus at mi placerat dapibus.
%\end{zitemize}